---
title:
output:  
    html_document:
        toc: true
        self_contained: false
        includes:
            in_header: header.html
---


```{r initialization,echo=FALSE}
library(data.table)
library(formattable)
library(shiny)
library(knitr)
knitr::opts_chunk$set(echo=FALSE, warning=FALSE,messages=FALSE)
source("../missioncontrol.lib.R")
```



<style type="text/css">

.main-container {
  max-width:100%;
  margin:0;
  padding:0;
}
a.nohover  {
  pointer-events: none;
  }
pre.r {
    border:0;
    background:#ffffff !important;
    font-size: 11px;

}
  
</style>

```{r echo=FALSE}
makeActiveMenuBar("faq",generatedText = glue("Using data till {till}",till=dall.rel2[,max(date)]))
```

<div class = "row">
<div class = "col-md-6 col-md-offset-3">

## Introduction

We built a statistical model to estimate crash metrics from daily aggregated
telemetry data. Crash statistics are of two types: crash rate and crash
incidence. Crash Rate is defined as the ratio of total crashes (of a given type
e.g. browser crash or content crash) to the total active hours of the users that
crashed (not all users). For example a crash rate of 1.24 can be understood as
"among the profiles that crashed, on average they crashed 1.24 times per active
hour of use". We also modeled the likelihood of a profile crashing (the 'crash
incidence') is the probability a profile experiences a crash. Together we get a
complete picture: what is the likelihood of a profile experiencing a crash and
given they do with what intensity do they crash?

## Model Input

Every channel is treated separately but the terminology is common. A version is
released, people update to it, and the previous version becomes mostly
unused(except ESR). As a new release e.g. Beta 78.0b17 is rolled out, we see
increased adoption. During the initial stages of rollout when adoption is low,
we have noticed increased variability in crash statistics. We use adoption as a
proxy for variability. Our model says that crash rate is essentially function of
OS and version, but the mean and variance is affected by adoption. A consequence
of this is once adoption has stabilized, we don't expect crash rates to change
much (assuming nothing in the underlying environment changes). See the end of
the page for the actual model.

## Page Layout

Every channel has a major and minor e.g. 66.0.1 has a 66 as its major and 0.1 as the minor. Similarly beta 67.0b16 has 67 as major and b16 as minor. For nightly, minors are YYYYMMDD.  

At the very top right you'll see the latest data being used. It should be up to
date Usage The page starts with a usage summary: • Which version is-current and
which version we compare to (the last version) ◦ For nightly the current one is
always one day old since the most recent has way too little adoption to be
meaningful • The adoption (percent of total Firefox active hours on current
version) and the # of profiles that crashed and total number of profiles on this
version ◦ Having tangible numbers like # of profiles make adoption more
meaningful. Sometimes have only a few hundred profiles on a channel/release
making any crash statistics doubtful

### Crash Rates and Crash Incidence

Each row an OS, we list three columns:

- Total crash rate which is the sum of browser and content 
- Browser crash rate which is defined as total browser crashes per active hour for profiles experiencing content crashes
- Content crash rate which is defined as total content crashes per active hour for profiles experiencing content crashes

Within each cell we see the crash rate and the relative change wrt to previous version in parenthesis.  These cells are color coded

- If we are  more than 70% sure that  that the relative change is worse than 20% : RED. A definite change for the worse
- If we are  between than 50 .. 70% sure that  that the relative change is more than 20% : ORANGE.  Worrying but need more data
- If we are  more than 70% sure that  that the relative change is better than 20% : GREEN. A definite change for the better
- Otherwise grey: which could mean no change or not  enough data


### Evolution Figures

For every version, we plot the median estimated crash rate for the duration that
version was 'current'. The error bars correspond to 90% credible
intervals. Hovering over the points will reveal more information. Generally
older versions will change much but the current one will as new data comes in.,
which will change all the estimates of data on the current version.

### Rollout Figure

For release only, we plot crash rates vs adoption for both current and previous
versions.  If we are more than 70% sure of ourselves, the points have a triangle
pointing upward indicating a regression or a triangle pointing downwards
indicating improvement .

## How is Relative Difference Computed?
To make a an apple to apple comparison, when the current version has reached
e.g. 5% adoption, we estimate what the crash rate would have been when the
previous version had reached 5%. Sometimes this requires interpolation given the
differing ways versions reach adoption levels.


## What Model are You Using?

Best understood from the following
[`brms`](https://cran.r-project.org/package=brms) snippet

For all channels except Nightly, the crash rate is


```{r eval=FALSE,echo=TRUE}

  cmain+1 |cmain > 0  ~ os + offset(log( crash active hours+1/60)) + (1+os|c_version)  + s(nvc,m=1,by=os)
               shape  ~ os+s(nvc,m=1)
               family ~ negbinomial()

```


For nightly, it is



```{r eval=FALSE,echo=TRUE}

   cmain+1 |cmain > 0 ~ os + offset(log(crash active hours+ 1/60)) + (1+os | c_version) + s(nvc, m = 1)
                shape ~ log(dau_cversion + 1) + os
               family ~ negbinomial()

```

For crash incidence (note we ideally this should be some beta-binomial model
since the following model can theoretically produce proportions larger than 1)


```{r eval=FALSE,echo=TRUE}
   log(1+crashing dau) ~ os + offset(log( dau on current version)) + s(nvc,m=1,by=os) + (1+os|c_version)
                sigma  ~ os + s(nvc,m=1)
               family  ~ gaussian
```

and for nightly


```{r eval=FALSE,echo=TRUE}
   log(1+crashing dau) ~ os + offset(log( dau on current version)) +  s(nvc, m = 1) + (1+os|c_version)
                sigma  ~ os + nvc
               family  ~ gaussian
```

</div>
</div>
