---
title: 
output:  
    html_document:
        self_contained: false
        includes:
            in_header: header.html
params:
    dest: "moco"

---


```{r initialization,echo=FALSE}
library(data.table)
library(formattable)
library(shiny)
library(knitr)
knitr::opts_chunk$set(echo=FALSE, warning=FALSE,messages=FALSE)

```



<style type="text/css">

.main-container {
  max-width:100%;
  margin:0;
  padding:0;
}
a.nohover  {
  pointer-events: none;
  }
</style>

```{r echo=FALSE}
currentVersion <- c(name=nightly.current.vs.previous$Windows_NT$versiona,
                    days = dall.nightly2[os=='Windows_NT' & c_version ==nightly.current.vs.previous$Windows_NT$versiona, .N])

olderVersion <- c(name=nightly.current.vs.previous$Windows_NT$versionb,
                    days = dall.nightly2[os=='Windows_NT' & c_version ==nightly.current.vs.previous$Windows_NT$versionb, .N])
makeActiveMenuBar("nightly",generatedText = glue("Using data till {till}, render time: {wh} UTC",till=dall.nightly2[,max(date)],wh=strftime(gen.time,"%c" )))
```



<div class = "row" style='text-align:center;'>
<div class = "col-md-6 col-md-offset-3">
<b>Current version</b>: `r currentVersion['name']` (`r Plural(currentVersion['days'],'day')`  of data) <b>Other version</b>: `r olderVersion['name']` (`r Plural(olderVersion['days'],'day')` of data)
</div>
</div>


<div class = "row" style='text-align:center;'>
<div class = "col-md-6 col-md-offset-3">
<b> Take results from products with less than 10% adoption with several pinches
of salt</b>
</div>
</div>


<div class = "row">

<div class = "col-md-2 col-md-offset-3">
<h2>Usage</h2>
<p class='notes'> Crasher is a profile that crashed(content and/or browser).</p>
</div>
<div class = "col-md-4">
```{r echo=FALSE}
makeUsageTable(nightly.usage$usage,params$dest)
```
</div>

</div>



<div class = "row">
<div class = "col-md-2 col-md-offset-3">
<h2>Crash Rate</h2>
<div class='notes'>
<p>Crash Rates(Relative Change % wrt 'Other Version')<p>
<p> <font color='red'>Red</font> is BAD (more than 75% confident of a >20% regression </p>
<p> <font color='darkorange'>Orange</font> is WORRYING (60-75% confident of >20% regression </p>
<p> Grey is NO CHANGE</p>
<p> <font color='limegreen'>Green</font> is definite IMPROVEMENT (more than 75% confident of >20%    improvement</p>
</div>
</div>
<div class = "col-md-4">
```{r echo=FALSE}
nightly.summary$rate
```
</div>
</div>

<div class = "row">
<div class = "col-md-2 col-md-offset-3">
<h2>Crash Incidence</h2>
</div>
<div class = "col-md-4">
```{r echo=FALSE}
nightly.summary$incidence
```
</div>
</div>

<div class = "row">
<div class = "col-md-6 col-md-offset-3">
<h2> Evolution</h2>
<ul class="nav nav-tabs" role="tablist">
 <li class="active"><a href="#nightly_win_evo"  role="tab" data-toggle="tab" >Windows</a></li>
 <li><a href="#nightly_darwin_evo"  role="tab" data-toggle="tab">Darwin</a></li>
 <li><a href="#nightly_linux_evo"  role="tab" data-toggle="tab" >Linux</a></li>  
</ul>
</div>
</div>

<div class = "row">
<div class = "col-md-8 col-md-offset-2">
<br/>
<div class="tab-content">

<div id="nightly_win_evo" class="tab-pane fade in active">
<div class = "col-md-12">
```{r}
NE.W <- 1000
makeEvolutionFigure(nightly.evolution,'Windows_NT',"Browser Crash Rate  for Nightly, Windows_NT","rate",whi="cmr",
                    height=240,width=NE.W,showAction=TRUE,pointSize=40)
```
</div>
<div class = "col-md-12">
```{r}
makeEvolutionFigure(nightly.evolution,'Windows_NT',"Browser Crash Incidence % for Nightly, Windows_NT","incidence",
                    whi="cmi",height=240,width=NE.W,pointSize=40)
```
</div>
<div class = "col-md-12">
```{r}
makeEvolutionFigure(nightly.evolution,'Windows_NT',"Content Crash Rate  for Nightly, Windows_NT","rate",whi="ccr",height=240,
                    width=NE.W,pointSize=40)
```
</div>
<div class = "col-md-12">
```{r}
makeEvolutionFigure(nightly.evolution,'Windows_NT',"Content Crash Incidence % for Nightly, Windows_NT","incidence",whi="cci",height=240,
                    width=NE.W,pointSize=40)
```
</div>
</div>


<div id="nightly_darwin_evo" class="tab-pane fade in">
<div class = "col-md-12">
```{r}
makeEvolutionFigure(nightly.evolution,'Darwin',"Browser Crash Rate  for Nightly, Darwin","rate",whi="cmr",height=240,
                    width=NE.W,pointSize=40)
```
</div>
<div class = "col-md-12">
```{r}
makeEvolutionFigure(nightly.evolution,'Darwin',"Browser Crash Incidence % for Nightly, Darwin","incidence",whi="cmi",
                    height=240,width=NE.W,pointSize=40)
```
</div>
<div class = "col-md-12">
```{r}
makeEvolutionFigure(nightly.evolution,'Darwin',"Content Crash Rate  for Nightly, Darwin","rate",whi="ccr",height=240,width=NE.W
                    ,pointSize=40)
```
</div>
<div class = "col-md-12">
```{r}
makeEvolutionFigure(nightly.evolution,'Darwin',"Content Crash Incidence % for Nightly, Darwin","incidence",whi="cci",height=240,width=NE.W
                    ,pointSize=40)
```
</div>
</div>


<div id="nightly_linux_evo" class="tab-pane fade in">
<div class = "col-md-12">
```{r}
makeEvolutionFigure(nightly.evolution,"Linux","Browser Crash Rate  for Nightly, Windows_NT","rate",whi="cmr",height=240,width=NE.W,
                    pointSize=40,showAction=TRUE)
```
</div>
<div class = "col-md-12">
```{r}
makeEvolutionFigure(nightly.evolution,'Linux',"Browser Crash Incidence % for Nightly, Linux","incidence",whi="cmi",height=240,width=NE.W
                   ,pointSize=40)
```
</div>
<div class = "col-md-12">
```{r}
makeEvolutionFigure(nightly.evolution,'Linux',"Content Crash Rate  for Nightly, Linux","rate",whi="ccr",height=240,width=NE.W,
                    pointSize=40)
```
</div>
<div class = "col-md-12">
```{r}
makeEvolutionFigure(nightly.evolution,'Linux',"Content Crash Incidence % for Nightly, Linux","incidence",whi="cci",height=240,width=NE.W,
                    pointSize=40)
```
</div>
</div>


</div>
</div>
</div>

