---
title: BETA
output:
  html_document:
     theme: cosmo
---


```{r relstuff,echo=FALSE}
## We need the models produced from [./report.2.Rmd]. So run the code there first.
library(knitr)
library(kableExtra)
knitr::opts_chunk$set(echo=FALSE, warning=FALSE,messages=FALSE)
```



## Summary {.tabset}

AS OF NOW: `r max(beta.summary.1$date)`

- Current Version: `r beta.current.version`
  - Days Since Release: `r beta.current.data[os=='Windows_NT',.N]`
- Previous Version: `r beta.prev.version`


```{r echo=FALSE}
cmr.alert <- paste(as.character(beta.summary[, os[which(cmr.reg.prob>0.7)]]),collapse=",")
ccr.alert <- paste(as.character(beta.summary[, os[which(ccr.reg.prob>0.7)]]),collapse=",")
cmi.alert <- paste(as.character(beta.summary[, os[which(cmi.reg.prob>0.7)]]),collapse=",")
cci.alert <- paste(as.character(beta.summary[, os[which(ccr.reg.prob>0.7)]]),collapse=",")
cmr.alert.s <- if(nchar(cmr.alert) > 0) glue("<br/>at least 70% probability of regression in main crash rates for os: {cmr.alert}\n") else ""
ccr.alert.s  <- if(nchar(ccr.alert) > 0) glue("<br/>at least 70% probability of regression in content crash rates for os: {ccr.alert}\n") else ""
cmi.alert.s <- if(nchar(cmi.alert) > 0) glue("<br/>at least 70% probability of regression in main crash incidence for os: {cmi.alert}\n") else ""
cci.alert.s <- if(nchar(cci.alert) > 0) glue("<br/>at least 70% probability of regression in content crash incidence for os: {cci.alert}\n") else ""
if(any(nchar(c(cmr.alert.s, ccr.alert.s,cmi.alert.s,cci.alert.s)) > 0)){
  preamble <- glue("<br/><b>ALERT</b>: Some likely regressions:", cmr.alert.s,ccr.alert.s,cmi.alert.s,cci.alert.s)
}else preamble='<br/>'

kable_styling(
  kable(t(
    beta.summary.1[,list(os,
                      "% Active Hours Adoption"=round(nvc*100,2),
                      "Average" = round(cavgr.mean,3),
                      "Browser" = round(cmr.mean,3),
                      "Content" = round(ccr.mean,3),
                      "Average" = round(100*cavgi.mean,2),
                      "Browser" = round(100*cmi.mean,2),
                      "Content" = round(100*cci.mean,2)
                      )])[,c(3,1,2)]
   ,caption = "Current  Levels",full.width=FALSE,)
) %>% pack_rows("Adoption", 2, 2) %>% pack_rows("Crash Rate/Active Hr(For Crashers)", 3, 5) %>% pack_rows("Crash Incidence %", 6, 8)

```

```{r xo,results='asis'}
preamble
```

### Crash Rates

Defined as crashes per active hour for those profiles crashing

```{r}
library(rbokeh)
makeSummaryPlot <- function(dd,xlab,ylab,width=NULL){
  ylim <- dd$fac
  figure(ylim = ylim,width=if(is.null(width)) 330 else width,height=300) %>%
    ly_segments(lo90, fac, hi90, fac, data = dd ,color = NULL, width = 2) %>%
    ly_points(mn, fac, glyph = 16, data=dd,hover = list(value=mn,lo90=lo90,hi90=hi90,regressionProb=100*regProb)) %>%
    x_axis(label = xlab) %>%
    y_axis(label = ylab) %>%
    theme_axis(c("x", "y"), 
               axis_label_text_font_size = "8pt",
               major_label_text_font_size = "8pt")%>%
    theme_legend(background_fill_alpha=0) %>% theme_grid(c("x", "y"), grid_line_color = "white")
}
figs <- list(
  makeSummaryPlot(beta.summary.1[, list(fac=as.character(os),lo90=cavgr.lo90,mn=cavgr.mean,hi90=cavgr.hi90,regProb=cavgr.reg.prob)],
                  "Current Average Crash",""),
  makeSummaryPlot(beta.summary.1[, list(fac=as.character(os),lo90=cmr.lo90,mn=cmr.mean,hi90=cmr.hi90,regProb=cmr.reg.prob)],
                  "Current Browser Crash", ""),
  makeSummaryPlot(beta.summary.1[, list(fac=as.character(os),lo90=ccr.lo90,mn=ccr.mean,hi90=ccr.hi90,regProb=ccr.reg.prob)],
                "Current Content Crash","")
)
grid_plot(figs)
```

### Crash Incidence

Defined as percentage of DAU that experience a crash

```{r}
figs <- list(
  makeSummaryPlot(beta.summary.1[, list(fac=as.character(os),lo90=100*cmi.lo90,mn=100*cmi.mean,hi90=100*cmi.hi90,regProb=cmi.reg.prob)],
                  "Current Browser Crash", ""),
  makeSummaryPlot(beta.summary.1[, list(fac=as.character(os),lo90=100*cci.lo90,mn=100*cci.mean,hi90=100*cci.hi90,regProb=cci.reg.prob)],
                "Current Content Crash",""),
  makeSummaryPlot(beta.summary.1[, list(fac=as.character(os),lo90=100*cavgi.lo90,mn=100*cavgi.mean,hi90=100*cavgi.hi90,regProb=cavgi.reg.prob)],
                  "Current Average Crash","")
)
grid_plot(figs)
```



## Adoption


As this version rolls out, how does it compare to the previous version adjusting
for similar adoption levels?

```{r}
makeAdoptionPlot <- function(dita,cver,over,xlab,ylab){
  A <- dita[version==cver,][order(adoption),]
  B <- dita[version==over,][order(adoption),]
  AB <- rbind(A,B)
  figure(width=500,height=300) %>%
    ly_points(data=AB,adoption, mn, color=version,hover = AB) %>%
    ly_lines(data=AB,adoption, mn, color=version) %>%
    x_axis(label = xlab) %>%
    y_axis(label = ylab)%>%
    theme_legend(background_fill_alpha=0) %>% theme_grid(c("x", "y"), grid_line_color = "white")

}

makeRelPlot <- function(dita,xlab,ylab){
  dita <- dita[order(adoption),]
  figure(width=700,height=300) %>%
    ly_points(data=dita,adoption, mn, hover = dita) %>%
    ly_lines(data=dita,adoption, mn) %>%
    ly_polygons(data=dita, xs=c(adoption,rev(adoption)),ys=c(lo90,rev(hi90))) %>%
    x_axis(label = xlab) %>%
    y_axis(label = ylab)%>%
    theme_legend(background_fill_alpha=0) %>% theme_grid(c("x", "y"), grid_line_color = "white")

}

```


### Average Crash {.tabset}

#### Rates

```{r x4}
temp.t <- beta.posts.1[ccr.wt > 0 | cmr.wt > 0, list(os=os,date=date,version=c_version,adoption=nvc*100,lo90=cavgr.lo90,mn=cavgr.mean,hi90=cavgr.hi90,regProb=100*cavgr.reg.prob)]
figs4 <- list(
  makeAdoptionPlot(temp.t[os=='Windows_NT',] , cver=beta.current.version,over=beta.prev.version , xlab='Adoption %', ylab='Windows_NT'),
  makeAdoptionPlot(temp.t[os=='Darwin',] , cver=beta.current.version,over=beta.prev.version , xlab='Adoption %', ylab='Darwin'),
  makeAdoptionPlot(temp.t[os=='Linux',] , cver=beta.current.version,over=beta.prev.version , xlab='Adoption %', ylab='Linux'))

grid_plot(figs4)
```


#### Incidence Pct

```{r x3}
temp.t <- beta.posts.1[, list(os=os,date=date,version=c_version,adoption=nvc*100,lo90=100*cavgi.lo90,mn=100*cavgi.mean,hi90=100*cavgi.hi90,regProb=100*cavgi.reg.prob)]
figs5 <- list(
  makeAdoptionPlot(temp.t[os=='Windows_NT',] , cver=beta.current.version,over=beta.prev.version , xlab='Adoption %', ylab='Windows_NT'),
  makeAdoptionPlot(temp.t[os=='Darwin',] , cver=beta.current.version,over=beta.prev.version , xlab='Adoption %', ylab='Darwin'),
  makeAdoptionPlot(temp.t[os=='Linux',] , cver=beta.current.version,over=beta.prev.version , xlab='Adoption %', ylab='Linux'))

grid_plot(figs5)
```




### Browser Crash {.tabset}

#### Rates 
```{r x2}


figs1 <- list(
  makeAdoptionPlot(beta.posts.1[os=='Windows_NT' & cmr.wt > 0,
                           list(version=c_version,date=date,adoption=nvc*100,lo90=cmr.lo90,mn=cmr.mean,hi90=cmr.hi90,regProb=100*cmr.reg.prob)]
               , cver=beta.current.version,over=beta.prev.version
               , xlab='Adoption %', ylab='Windows_NT'
                 ),
  makeAdoptionPlot(beta.posts.1[os=='Darwin' & cmr.wt > 0,
                           list(version=c_version,date=date,adoption=nvc*100,lo90=cmr.lo90,mn=cmr.mean,hi90=cmr.hi90,regProb=100*cmr.reg.prob)]
               , cver=beta.current.version,over=beta.prev.version
               , xlab='Adoption %', ylab='Darwin'
                 ),
  makeAdoptionPlot(beta.posts.1[os=='Linux' & cmr.wt > 0,
                           list(version=c_version,date=date,adoption=nvc*100,lo90=cmr.lo90,mn=cmr.mean,hi90=cmr.hi90,regProb=100*cmr.reg.prob)]
               , cver=beta.current.version,over=beta.prev.version
               , xlab='Adoption %', ylab='Linux'
                 )
)
grid_plot(figs1)
```

#### Incidence Pct

```{r x1}
figs2 <- list(
              makeAdoptionPlot(beta.posts.1[os=='Windows_NT',
                           list(version=c_version,date=date,adoption=nvc*100,lo90=100*cmi.lo90,mn=100*cmi.mean,hi90=100*cmi.hi90,regProb=100*cmi.reg.prob)]
               , cver=beta.current.version,over=beta.prev.version
               , xlab='Adoption %', ylab='Windows_NT'
                 )             ,
              makeAdoptionPlot(beta.posts.1[os=='Darwin',
                           list(version=c_version,date=date,adoption=nvc*100,lo90=100*cmi.lo90,mn=100*cmi.mean,hi90=100*cmi.hi90,regProb=100*cmi.reg.prob)]
               , cver=beta.current.version,over=beta.prev.version
               , xlab='Adoption %', ylab='Darwin'
                 ),
              makeAdoptionPlot(beta.posts.1[os=='Linux',
                           list(version=c_version,date=date,adoption=nvc*100,lo90=100*cmi.lo90,mn=100*cmi.mean,hi90=100*cmi.hi90,regProb=100*cmi.reg.prob)]
               , cver=beta.current.version,over=beta.prev.version
               , xlab='Adoption %', ylab='Linux'
                 )
  
              )
grid_plot(figs2)
```





### Content Crash {.tabset}

#### Rates

```{r}
temp.t <- beta.posts.1[ccr.wt > 0, list(os=os,date=date,version=c_version,adoption=nvc*100,lo90=ccr.lo90,mn=ccr.mean,hi90=ccr.hi90,regProb=100*ccr.reg.prob)]
figs4 <- list(
  makeAdoptionPlot(temp.t[os=='Windows_NT',] , cver=beta.current.version,over=beta.prev.version , xlab='Adoption %', ylab='Windows_NT'),
  makeAdoptionPlot(temp.t[os=='Darwin',] , cver=beta.current.version,over=beta.prev.version , xlab='Adoption %', ylab='Darwin'),
  makeAdoptionPlot(temp.t[os=='Linux',] , cver=beta.current.version,over=beta.prev.version , xlab='Adoption %', ylab='Linux'))

grid_plot(figs4)
```


#### Incidence %

```{r }
temp.t <- beta.posts.1[, list(os=os,date=date,version=c_version,adoption=nvc*100,lo90=100*cci.lo90,mn=100*cci.mean,hi90=100*cci.hi90,regProb=100*cci.reg.prob)]
figs5 <- list(
  makeAdoptionPlot(temp.t[os=='Windows_NT',] , cver=beta.current.version,over=beta.prev.version , xlab='Adoption %', ylab='Windows_NT'),
  makeAdoptionPlot(temp.t[os=='Darwin',] , cver=beta.current.version,over=beta.prev.version , xlab='Adoption %', ylab='Darwin'),
  makeAdoptionPlot(temp.t[os=='Linux',] , cver=beta.current.version,over=beta.prev.version , xlab='Adoption %', ylab='Linux'))
grid_plot(figs5)
```




## Trends

This graph represents the final crash rate (at peak adoption) of a beta number
(e.g. `XYZ.bK`).  *Ideally* ought to decrease within a major number.

```{r}

makeBetaTrend <- function(dd,xlab,ylab,width=NULL){
  xlim <- dd$version
  figure(xlim = xlim,width=if(is.null(width)) 500 else width,height=300,legend_location='top_left') %>%
    ly_segments(version, lo90, version, hi90, data = dd ,color = major, width = 2) %>%
    ly_points(version, mn, glyph = 16, data=dd,color=major,hover = list(value=mn,lo90=lo90,hi90=hi90,adoption=adoption)) %>%
    x_axis(label = xlab) %>%
    y_axis(label = ylab) %>%
    theme_axis(c("x", "y"), 
               axis_label_text_font_size = "8pt",
               major_label_text_font_size = "8pt") %>%
    theme_axis("x",major_label_orientation = -90,
               axis_label_text_baseline='top'
               ) %>%
    theme_legend(background_fill_alpha=0) %>% theme_grid(c("x", "y"), grid_line_color = "white")
}

```


### Average Crash {.tabset id='trend-average'}


#### Rates

```{r}
t.temp <- beta.trend2[, list(os=as.character(os),adoption=100*nvc,version=as.character(c_version),major=as.character(major),lo90=cavgr.lo90,mn=cavgr.mean,hi90=cavgr.hi90)]
fig7 <- list(
  makeBetaTrend(t.temp[os=='Windows_NT',], xlab='Avg Crash', ylab='Windows_NT'),
  makeBetaTrend(t.temp[os=='Darwin',], xlab='Avg Crash', ylab='Darwin'),
  makeBetaTrend(t.temp[os=='Linux',], xlab='Avg Crash', ylab='Linux'))


grid_plot(fig7)
  
```

#### Incidence Pct

```{r}
t.temp <- beta.trend2[, list(os=as.character(os),adoption=100*nvc,version=as.character(c_version),major=as.character(major),lo90=100*cavgi.lo90,mn=100*cavgi.mean,hi90=100*cavgi.hi90)]
fig8 <- list(
  makeBetaTrend(t.temp[os=='Windows_NT',], xlab='Avg Crash', ylab='Windows_NT'),
  makeBetaTrend(t.temp[os=='Darwin',], xlab='Avg Crash', ylab='Darwin'),
  makeBetaTrend(t.temp[os=='Linux',], xlab='Avg Crash', ylab='Linux'))


grid_plot(fig8)
  
```



### Browser Crash {.tabset id='trend-main'}


#### Rates

```{r}
t.temp <- beta.trend2[, list(os=as.character(os),adoption=100*nvc,version=as.character(c_version),major=as.character(major),lo90=cmr.lo90,mn=cmr.mean,hi90=cmr.hi90)]
fig9 <- list(
  makeBetaTrend(t.temp[os=='Windows_NT',], xlab='Browser Crash', ylab='Windows_NT'),
  makeBetaTrend(t.temp[os=='Darwin',], xlab='Browser Crash', ylab='Darwin'),
  makeBetaTrend(t.temp[os=='Linux',], xlab='Browser Crash', ylab='Linux'))


grid_plot(fig9)
  
```

#### Incidence Pct

```{r}
t.temp <- beta.trend2[, list(os=as.character(os),adoption=100*nvc,version=as.character(c_version),major=as.character(major),lo90=100*cmi.lo90,mn=100*cmi.mean,hi90=100*cmi.hi90)]
fig10<- list(
  makeBetaTrend(t.temp[os=='Windows_NT',], xlab='Browser Crash', ylab='Windows_NT'),
  makeBetaTrend(t.temp[os=='Darwin',], xlab='Browser Crash', ylab='Darwin'),
  makeBetaTrend(t.temp[os=='Linux',], xlab='Browser Crash', ylab='Linux'))


grid_plot(fig10)
  
```


### Content Crash {.tabset id='trend-content'}


#### Rates

```{r}
t.temp <- beta.trend2[, list(os=as.character(os),adoption=100*nvc,version=as.character(c_version),major=as.character(major),lo90=ccr.lo90,mn=ccr.mean,hi90=ccr.hi90)]
fig9 <- list(
  makeBetaTrend(t.temp[os=='Windows_NT',], xlab='Content Crash', ylab='Windows_NT'),
  makeBetaTrend(t.temp[os=='Darwin',], xlab='Content Crash', ylab='Darwin'),
  makeBetaTrend(t.temp[os=='Linux',], xlab='Content Crash', ylab='Linux'))


grid_plot(fig9)
  
```

#### Incidence Pct

```{r}
t.temp <- beta.trend2[, list(os=as.character(os),adoption=100*nvc,version=as.character(c_version),major=as.character(major),lo90=100*cci.lo90,mn=100*cci.mean,hi90=100*cci.hi90)]
fig10<- list(
  makeBetaTrend(t.temp[os=='Windows_NT',], xlab='Content Crash', ylab='Windows_NT'),
  makeBetaTrend(t.temp[os=='Darwin',], xlab='Content Crash', ylab='Darwin'),
  makeBetaTrend(t.temp[os=='Linux',], xlab='Content Crash', ylab='Linux'))


grid_plot(fig10)
  
```


