---
title: RELEASE
output:
  html_document:
     theme: cosmo
---


```{r relstuff,echo=FALSE}
## We need the models produced from [./report.2.Rmd]. So run the code there first.
library(knitr)
library(kableExtra)
knitr::opts_chunk$set(echo=FALSE, warning=FALSE,messages=FALSE)
```



## Summary {.tabset}

AS OF NOW: `r max(rel.summary$date)`

- Current Version: `r rel.current.version`
  - Days Since Release: `r rel.current.data[os=='Windows_NT',.N]`
- Previous Version: `r rel.prev.version`


```{r x1,echo=FALSE}
kable_styling(
  kable(t(
    rel.summary[,list(os,
                      "% Active Hours Adoption"=round(nvc*100,2),
                      "Browser" = round(cmr.mean,3),
                      "Content" = round(ccr.mean,3),
                      "Average" = round(cavgr.mean,3),
                      "Browser" = round(100*cmi.mean,2),
                      "Content" = round(100*cci.mean,2),
                      "Average" = round(100*cavgi.mean,2)
                      )])
   ,caption = "Current  Levels",full.width=FALSE,)
) %>% pack_rows("Adoption", 2, 2) %>% pack_rows("Crash Rate/Active Hr", 3, 5) %>% pack_rows("Crash Incidence %", 6, 8)
```

### Crash Rates

Defined as crashes per active hour for those profiles crashing

```{r x2}
library(rbokeh)
makeSummaryPlot <- function(dd,xlab,ylab,width=NULL){
  ylim <- dd$fac
  figure(ylim = ylim,width=if(is.null(width)) 330 else width,height=300) %>%
    ly_segments(lo90, fac, hi90, fac, data = dd ,color = NULL, width = 2) %>%
    ly_points(mn, fac, glyph = 16, data=dd,hover = list(value=mn,lo90=lo90,hi90=hi90)) %>%
    x_axis(label = xlab) %>%
    y_axis(label = ylab) %>%
    theme_axis(c("x", "y"), 
               axis_label_text_font_size = "8pt",
               major_label_text_font_size = "8pt")
}
figs <- list(
  makeSummaryPlot(rel.summary[, list(fac=as.character(os),lo90=cmr.lo90,mn=cmr.mean,hi90=cmr.hi90)],
                  "Current Browser Crash", ""),
  makeSummaryPlot(rel.summary[, list(fac=as.character(os),lo90=ccr.lo90,mn=ccr.mean,hi90=ccr.hi90)],
                "Current Content Crash",""),
  makeSummaryPlot(rel.summary[, list(fac=as.character(os),lo90=cavgr.lo90,mn=cavgr.mean,hi90=cavgr.hi90)],
                  "Current Average Crash","")
)
grid_plot(figs)
```

### Crash Incidence

Defined as percentage of DAU that experience a crash

```{r x3}
figs <- list(
  makeSummaryPlot(rel.summary[, list(fac=as.character(os),lo90=100*cmi.lo90,mn=100*cmi.mean,hi90=100*cmi.hi90)],
                  "Current Browser Crash", ""),
  makeSummaryPlot(rel.summary[, list(fac=as.character(os),lo90=100*cci.lo90,mn=100*cci.mean,hi90=100*cci.hi90)],
                "Current Content Crash",""),
  makeSummaryPlot(rel.summary[, list(fac=as.character(os),lo90=100*cavgi.lo90,mn=100*cavgi.mean,hi90=100*cavgi.hi90)],
                  "Current Average Crash","")
)
grid_plot(figs)
```




## Adoption


As this version rolls out, how does it compare to the previous version adjusting
for similar adoption levels?

```{r x4}
makeAdoptionPlot <- function(dita,cver,over,xlab,ylab){
  A <- dita[version==cver,][order(adoption),]
  B <- dita[version==over,][order(adoption),]
  AB <- rbind(A,B)
  figure(width=500,height=300) %>%
    ly_points(data=AB,adoption, mn, color=version,hover = AB) %>%
    ly_lines(data=AB,adoption, mn, color=version) %>%
    x_axis(label = xlab) %>%
    y_axis(label = ylab)

}

makeRelPlot <- function(dita,xlab,ylab){
  dita <- dita[order(adoption),]
  figure(width=700,height=300) %>%
    ly_points(data=dita,adoption, mn, hover = dita) %>%
    ly_lines(data=dita,adoption, mn) %>%
    ly_polygons(data=dita, xs=c(adoption,rev(adoption)),ys=c(lo90,rev(hi90))) %>%
    x_axis(label = xlab) %>%
    y_axis(label = ylab)

}

```


#### Average Crash {.tabset}

##### Rates

```{r x5}
temp.t <- rel.posts[cmr.wt > 0 |ccr.wt > 0, list(os=os,date=date,version=c_version,adoption=nvc*100,lo90=cavgr.lo90,mn=cavgr.mean,hi90=cavgr.hi90,regProb=cavgr.reg.prob*100)]
figs4 <- list(makeAdoptionPlot(temp.t[os=='Windows_NT',] , cver=rel.current.version,over=rel.prev.version , xlab='Adoption %', ylab='Windows_NT'),
              makeAdoptionPlot(temp.t[os=='Darwin',] , cver=rel.current.version,over=rel.prev.version , xlab='Adoption %', ylab='Darwin'),
              makeAdoptionPlot(temp.t[os=='Linux',] , cver=rel.current.version,over=rel.prev.version , xlab='Adoption %', ylab='Linux')
              )
grid_plot(figs4)
```


##### Incidence Pct

```{r x6}
temp.t <- rel.posts[, list(os=os,date=date,version=c_version,adoption=nvc*100,lo90=100*cavgi.lo90,mn=100*cavgi.mean,hi90=100*cavgi.hi90,regProb=100*cavgi.reg.prob)]
figs5 <- list(makeAdoptionPlot(temp.t[os=='Windows_NT',] , cver=rel.current.version,over=rel.prev.version , xlab='Adoption %', ylab='Windows_NT'),
              makeAdoptionPlot(temp.t[os=='Darwin',] , cver=rel.current.version,over=rel.prev.version , xlab='Adoption %', ylab='Darwin'),
              makeAdoptionPlot(temp.t[os=='Linux',] , cver=rel.current.version,over=rel.prev.version , xlab='Adoption %', ylab='Linux')
              )
grid_plot(figs5)
```



#### Browser Crash {.tabset}

##### Rates 
```{r x7}


figs1 <- list(
              makeAdoptionPlot(rel.posts[os=='Windows_NT' & cmr.wt > 0,
                           list(version=c_version,date=date,adoption=nvc*100,lo90=cmr.lo90,mn=cmr.mean,hi90=cmr.hi90,regProb=100*cmr.reg.prob)]
               , cver=rel.current.version,over=rel.prev.version
               , xlab='Adoption %', ylab='Windows_NT'
                 ),
              makeAdoptionPlot(rel.posts[os=='Darwin' & cmr.wt > 0,
                           list(version=c_version,date=date,adoption=nvc*100,lo90=cmr.lo90,mn=cmr.mean,hi90=cmr.hi90,regProb=100*cmr.reg.prob)]
               , cver=rel.current.version,over=rel.prev.version
               , xlab='Adoption %', ylab='Darwin'
                 ),
                makeAdoptionPlot(rel.posts[os=='Linux' & cmr.wt > 0,
                           list(version=c_version,date=date,adoption=nvc*100,lo90=cmr.lo90,mn=cmr.mean,hi90=cmr.hi90,regProb=100*cmr.reg.prob)]
               , cver=rel.current.version,over=rel.prev.version
               , xlab='Adoption %', ylab='Linux'
                 )

              )
grid_plot(figs1)
```

##### Incidence Pct

```{r x8}
figs2 <- list(
              makeAdoptionPlot(rel.posts[os=='Windows_NT',
                           list(version=c_version,date=date,adoption=nvc*100,lo90=100*cmi.lo90,mn=100*cmi.mean,hi90=100*cmi.hi90,regProb=100*cmi.reg.prob)]
               , cver=rel.current.version,over=rel.prev.version
               , xlab='Adoption %', ylab='Windows_NT'
                 ),
              makeAdoptionPlot(rel.posts[os=='Darwin',
                           list(version=c_version,date=date,adoption=nvc*100,lo90=100*cmi.lo90,mn=100*cmi.mean,hi90=100*cmi.hi90,regProb=100*cmi.reg.prob)]
               , cver=rel.current.version,over=rel.prev.version
               , xlab='Adoption %', ylab='Darwin'
                 ),
                            makeAdoptionPlot(rel.posts[os=='Linux',
                           list(version=c_version,date=date,adoption=nvc*100,lo90=100*cmi.lo90,mn=100*cmi.mean,hi90=100*cmi.hi90,regProb=100*cmi.reg.prob)]
               , cver=rel.current.version,over=rel.prev.version
               , xlab='Adoption %', ylab='Linux'
                 )

              )
grid_plot(figs2)
```



#### Content Crash {.tabset}

##### Rates

```{r x9}
temp.t <- rel.posts[ccr.wt > 0, list(os=os,date=date,version=c_version,adoption=nvc*100,lo90=ccr.lo90,mn=ccr.mean,hi90=ccr.hi90,regProb=100*ccr.reg.prob)]
figs4 <- list(
  makeAdoptionPlot(temp.t[os=='Windows_NT',] , cver=rel.current.version,over=rel.prev.version , xlab='Adoption %', ylab='Windows_NT'),
  makeAdoptionPlot(temp.t[os=='Darwin',] , cver=rel.current.version,over=rel.prev.version , xlab='Adoption %', ylab='Darwin'),
  makeAdoptionPlot(temp.t[os=='Linux',] , cver=rel.current.version,over=rel.prev.version , xlab='Adoption %', ylab='Linux')
)
             
grid_plot(figs4)
```


##### Incidence %

```{r}
temp.t <- rel.posts[, list(os=os,date=date,version=c_version,adoption=nvc*100,lo90=100*cci.lo90,mn=100*cci.mean,hi90=100*cci.hi90,regProb=100*cci.reg.prob)]
figs5 <- list(
  makeAdoptionPlot(temp.t[os=='Windows_NT',] , cver=rel.current.version,over=rel.prev.version , xlab='Adoption %', ylab='Windows_NT'),
  makeAdoptionPlot(temp.t[os=='Darwin',] , cver=rel.current.version,over=rel.prev.version , xlab='Adoption %', ylab='Darwin'),
  makeAdoptionPlot(temp.t[os=='Linux',] , cver=rel.current.version,over=rel.prev.version , xlab='Adoption %', ylab='Linux')
)

              
grid_plot(figs5)
```





## Trends

Long term view across versions, removing points where adoption is less than 10%
(i.e. first few days of release) which improves graph legibility.



```{r}
makeTrend <- function(dita,xlab,ylab,markers=NULL){
  dita <- dita[order(date),]
  f <- figure(width=500,height=300) %>%
    ly_points(data=dita,date, mn, hover = dita,size=8) %>%
    ly_lines(data=dita,date, smooth,width=2) %>%
    x_axis(label = xlab) %>%
    y_axis(label = ylab)
  if(!is.null(markers)){
    f <-ly_abline(f,v=(markers$x),color='grey',line_dash=3)
  }
  f %>% theme_grid(c("x", "y"), grid_line_color = "white")
}
```

```{r}
rel.dates.versions <- rel.posts[,.SD[1,list(x=as.Date(date))],by=list(y=c_version)]
```

### Average Crash {.tabset id='trend-average'}
#### Rates

```{r}
t.temp <- rel.posts[nvc > 0.1,][, list(os,date=as.Date(date),version=c_version, mn.orig=(cmr+ccr)/2*100, mn = cavgr.mean,lo90=cavgr.lo90, hi90=cavgr.hi90,smooth=cavgr.loess)]
fig7 <- list( makeTrend(t.temp[os=='Windows_NT',], xlab='Date',ylab='Windows_NT',markers=rel.dates.versions),
             makeTrend(t.temp[os=='Darwin',], xlab='Date',ylab='Darwin',markers=rel.dates.versions),
             makeTrend(t.temp[os=='Linux',], xlab='Date',ylab='Linux',markers=rel.dates.versions))
            
grid_plot(fig7)
```

#### Incidence Pct
```{r}
t.temp <- rel.posts[nvc > 0.1,][, list(os,date=as.Date(date),version=c_version, mn.orig=(cmi+cci)/2*100, mn = 100*cavgi.mean,lo90=100*cavgi.lo90, hi90=100*cavgi.hi90,smooth=100*cavgi.loess)]
fig8 <- list(makeTrend(t.temp[os=='Windows_NT',], xlab='Date',ylab='Windows_NT',markers=rel.dates.versions),
             makeTrend(t.temp[os=='Darwin',], xlab='Date',ylab='Darwin',markers=rel.dates.versions),
             makeTrend(t.temp[os=='Linux',], xlab='Date',ylab='Linux',markers=rel.dates.versions))
             
grid_plot(fig8)
```


### Browser Crash {.tabset id='trend-main'}
#### Rates

```{r}
t.temp <- rel.posts[nvc > 0.1,][, list(os,date=as.Date(date),version=c_version, mn.orig=cmr, mn = cmr.mean,lo90=cmr.lo90, hi90=cmr.hi90,smooth=cmr.loess)]
fig9 <- list(
  makeTrend(t.temp[os=='Windows_NT',], xlab='Date',ylab='Windows_NT',markers=rel.dates.versions),
  makeTrend(t.temp[os=='Darwin',], xlab='Date',ylab='Darwin',markers=rel.dates.versions),
  makeTrend(t.temp[os=='Linux',], xlab='Date',ylab='Linux',markers=rel.dates.versions))


grid_plot(fig9)
```

#### Incidence Pct
```{r}
t.temp <- rel.posts[nvc > 0.1,][, list(os,date=as.Date(date),version=c_version, mn.orig=cmi, mn = 100*cmi.mean,lo90=100*cmi.lo90, hi90=100*cmi.hi90,smooth=100*cmi.loess)]
fig10 <- list(
  makeTrend(t.temp[os=='Windows_NT',], xlab='Date',ylab='Windows_NT',markers=rel.dates.versions),
  makeTrend(t.temp[os=='Darwin',], xlab='Date',ylab='Darwin',markers=rel.dates.versions),
  makeTrend(t.temp[os=='Linux',], xlab='Date',ylab='Linux',markers=rel.dates.versions))


grid_plot(fig10)
```



### Content Crash {.tabset id='trend-content'}
#### Rates

```{r}
t.temp <- rel.posts[nvc > 0.1,][, list(os,date=as.Date(date),version=c_version, mn.orig=ccr, mn = ccr.mean,lo90=ccr.lo90, hi90=ccr.hi90,smooth=ccr.loess)]
fig11 <- list(
  makeTrend(t.temp[os=='Windows_NT',], xlab='Date',ylab='Windows_NT',markers=rel.dates.versions),
  makeTrend(t.temp[os=='Darwin',], xlab='Date',ylab='Darwin',markers=rel.dates.versions),
  makeTrend(t.temp[os=='Linux',], xlab='Date',ylab='Linux',markers=rel.dates.versions))

grid_plot(fig11)
```

#### Incidence Pct
```{r}
t.temp <- rel.posts[nvc > 0.1,][, list(os,date=as.Date(date),version=c_version, mn.orig=cci, mn = 100*cci.mean,lo90=100*cci.lo90, hi90=100*cci.hi90,smooth=100*cci.loess)]
fig12 <- list(
  makeTrend(t.temp[os=='Windows_NT',], xlab='Date',ylab='Windows_NT',markers=rel.dates.versions),
  makeTrend(t.temp[os=='Darwin',], xlab='Date',ylab='Darwin',markers=rel.dates.versions),
  makeTrend(t.temp[os=='Linux',], xlab='Date',ylab='Linux',markers=rel.dates.versions))

grid_plot(fig12)
```
